Aa Language Reference Manual

### 2018-10-31 v2/Ahir-asm/devel/docs/AaLRM.tex
AaLrm modified to reflect change in macro-module handling.

\section{Module classes: pipeline, volatile, operator, inline, macro, foreign }

@@

\subsection{Inlined Modules}

An inlined module is substituted into the
point of a call to it in a three-step manner.
The input arguments are sampled at the point
of the call, the body of
the module is invoked and the output arguments
are transferred.  The semantics of an inlined
function call are defined by this three step
procedure.  The input arguments are sampled
at the point of the call, and the output
arguments are updated at the termination of
the call.

For example, the following
program 
\begin{verbatim}
$inline $module [add] $in (a: $uint<32> b: $uint<32>)
    $out (c: $uint<32>) $is
{
    c := (a+b)
}

$module [add_check] $in (p: $uint<32> q: $uint<32>) 
    $out (r : $uint<32>) $is
{
    $call add (p q) (r)
}
\end{verbatim}
is translated to
\begin{verbatim}
$module [add_check]
$in ( p : $uint<32>   q : $uint<32>  )
$out ( r : $uint<32>  )
$is
{
  $seriesblock[add_18] 
  {
    $parallelblock[InArgs] 
    {
      add_18_a := p
      add_18_b := q
    }
    ( add_18_a => add_18_a add_18_b => add_18_b )
    $seriesblock[body] 
    {
      add_18_c := (add_18_a + add_18_b)
    }
    (  add_18_c => add_18_c )
    $parallelblock[OutArgs] 
    {
      r := add_18_c
    }
    ( r => r )
  }
  ( r => r )
}
\end{verbatim}
The three step substitution of add into add\_check
is clearly seen.  
There are no restrictions on the
module that is being inlined.

@@

\end{verbatim}
is equivalent to 
\begin{verbatim}
$pipe  inpipe : $uint<32>  $depth 1 
$pipe  midpipe : $uint<32>  $depth 1 
$pipe  outpipe : $uint<32>  $depth 1 
$module [shift_check]
$in ()
$out ()
$is
{
  $seriesblock[shift_14] 
  {
    midpipe := inpipe
  }
  $seriesblock[shift_17] 
  {
    outpipe := midpipe
  }
}
\end{verbatim}
The two calls to shift are replaced by
series blocks with input/output arguments
replaced by the expressions passed to them
at the point of the call.

@@

There are no restrictions on the
module that is being inlined.

>>>>

\section{Module classes: pipeline, volatile, operator,  macro, foreign }

@@

@@

\end{verbatim}
is equivalent to 
\begin{verbatim}
$pipe  inpipe : $uint<32>  $depth 1 
$pipe  midpipe : $uint<32>  $depth 1 
$pipe  outpipe : $uint<32>  $depth 1 
$module [shift_check]
$in ()
$out ()
$is
{
    midpipe := inpipe
    outpipe := midpipe
}
\end{verbatim}
The two calls to shift are replaced by
the body of the shift module with input/output arguments
replaced by the expressions passed to them
at the point of the call.

@@

Macro modules should consist of only assignment
statements and call statements.  There should
be no object declarations inside a macro module.
